%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kamil K Wojcicki
\documentclass[margin,line]{templates/resume}
\usepackage{color,hyperref}
%\usepackage{color,soul}
\usepackage{comment} 
\usepackage{paralist}
\usepackage{enumitem}
%\usepackage{fancyhdr}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.6}
\definecolor{verydarkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=black,urlcolor=black,
            anchorcolor=black,citecolor=black}
\newcommand{\myhref}[3][blue]{\href{#2}{\color{#1}{#3}}}
\newcommand{\myhrefgray}[3][blue]{\href{#2}{\color{#1}{#3}}}
\newcommand{\compresslist}{%
\setlength{\itemsep}{3pt}%
\setlength{\parskip}{0pt}%
\setlength{\parsep}{0pt}%
}
%______________________________________________________________________________________________________________________
\begin{document}
\renewcommand{\thefootnote}{\fnsymbol{footnote}} 	
\name{\huge Shashank Gupta}

\begin{resume}
%\pagenumbering{arabic}
%\setcounter{page}{1}
    %__________________________________________________________________________________________________________________
    % Contact Information
%     \section{\mysidestyle Contact\\Information}
% Final Year Dual Degree Student,																	\hfill e-mail: {\href{mailto:ujain@iitk.ac.in}{\nolinkurl{ujain@iitk.ac.in}}}   \vspace{0mm}\\\vspace{0mm}%
%     \href{http://www.iitk.ac.in/ee/}{Department of Electrical Engineering}                            \hfill {\href{mailto:unnatjain@gmail.com}{\nolinkurl{unnatjain@gmail.com}}}  \vspace{0mm}\\\vspace{0mm}%
%     \href{http://www.iitk.ac.in/}{Indian Institute of Technology, Kanpur}                         \hfill Mobile: +91 8765173814 \vspace{0mm}\\\vspace{0mm}Kanpur 208016, India.\hfill Homepage: {\href{http://home.iitk.ac.in/~ujain/}{ \nolinkurl{home.iitk.ac.in/~ujain/}}} 
%     \vspace{0mm}\\\vspace{-4.5mm}%
    
    \section{\mysidestyle Basic\\Information}
\textbf{Graduating:} August, 2018
																	\hfill{\href{mailto:sgupta96@illinois.edu}{\nolinkurl{sgupta96@illinois.edu}}}   \vspace{0mm}\\\vspace{0mm}%
    \textbf{Visa Status:} F1 Student (Eligible for OPT)                            \hfill (+1) 217-904-6006  \vspace{0mm}\\\vspace{0mm}%
    \textbf{Citizenship:} India                         \hfill \myhref[black]{https://shatu.github.io/}{\nolinkurl{https://shatu.github.io/}}
    \vspace{0mm}\\\vspace{-4.5mm}%
%\line(1,0){440}
%\cfoot{asdf}
  %__________________________________________________________________________________________________________________
    % Education
\vspace{-0.1cm}    
\section{\mysidestyle Education}
    \textbf{\href{https://cs.illinois.edu/}{University of Illinois at Urbana Champaign}}\hfill {\textbf{Aug'15 -- Aug'18 (expected)}}
    \begin{itemize}[leftmargin=*]\compresslist
        \item[]Master of Science, Computer Science \hfill {\textbf{3.83/4.0}}\\
    \textbf{Thesis Adviser:} \href{http://www.cis.upenn.edu/~danroth/}{Prof. Dan Roth}
    \end{itemize}
    \vspace{-0.2cm}
    \textbf{\href{http://www.bits-pilani.ac.in/}{Birla Institute of Technology and Science, Pilani, India}}\hfill{\textbf{Aug'08 -- June'12}}
    \begin{itemize}[leftmargin=*]\compresslist
        \item[]Bachelor of Engineering (Hons.), Computer Science \hfill{\textbf{3.42/4.0}}
    \end{itemize}

%__________________________________________________________________________________________________________________
    % Research Interests
\vspace{-0.1cm}    
\section{\mysidestyle Research Interests}

%\begin{itemize}
%\itemsep0pt \item

%\begin{itemize}
%\item {\small Primarily in the areas concerning\\ 
\textbf{Natural Language Processing:} Question Answering; Dialogue Systems; Abstractive Summarization; Language Generation; (Sent./Doc.) Representation Learning. \\
\textbf{Machine Learning:} Deep Structured Models; Deep Generative Models; Distributed ML; Deep Reinforcement Learning, Model Interpretability \& Adversarial Attacks.
%\item {\small Worked in the areas of Planetary Ring Dynamics, Orbital Mechanics \& Control, and Space Propulsion.}
%\end{itemize}		 
%\end{itemize}

\vspace{-0.1cm}    
\section{\mysidestyle Technical\\ Skills}
\textbf{Languages:} \textit{Proficient}: Python, Java $|$ \textit{Basic}: C, C++, SQL, HTML/CSS, JavaScript, JSP/Servlets \\
\textbf{Toolkits:} Tensorflow, Hadoop, Pig, CogComp-NLP, Illinois-SL, Matlab, LaTeX

\vspace{-0.1cm}
\section{\mysidestyle Publications}
\vspace{0mm}
%\begin{itemize}[leftmargin=*]\compresslist
%\item 
\textbf{Shashank Gupta}, Varun Chandramouli and Soumen Chakrabarti. \textit{``Web-scale Entity Annotation Using MapReduce"}. In: High Performance Computing \textbf{(HiPC), 2013}\hfill{[\myhref[darkblue]{https://shatu.github.io/papers/Web-scale_Entity_Annotation_Using_MapReduce.pdf}{PDF}]}
%\end{itemize}

\vspace{-0.1cm}
\section{\mysidestyle Research Experience} 
\textsf{\textbf{Research Assistant:}}
\begin{itemize}[leftmargin = 0.7cm]\compresslist
\item~\textbf{UIUC}: \href{http://cogcomp.org/}{Cognitive Computation Group} \hfill{\small\textit{(Aug'15 - Dec'17)}} \vspace{-1mm}
\begin{itemize}[leftmargin=*]\compresslist
        \item[]\small\textit{Themes: Unsupervised Text Classification; Text Generation; Structured Learning}
    \end{itemize}
  
\item~\textbf{Max Planck Institute (MPI)}, \href{https://www.mpi-inf.mpg.de/departments/databases-and-information-systems/}{Databases \& Info. Sys. Group}  \hfill{\small\textit{(Aug'14 - April'15)}}
\vspace{-1mm}
\begin{itemize}[leftmargin=*]\compresslist
        \item[]\small\textit{Themes: Named Entity Disambiguation; KB Construction}
    \end{itemize}

\item~\textbf{IIT-Bombay}: \href{http://www.cse.iitb.ac.in/infolab}{InfoLab} \hfill{\small\textit{(Jan'13 - June'14)}}
\vspace{-1mm}
\begin{itemize}[leftmargin=*]\compresslist
        \item[]\small\textit{Themes: Entity Search} \&\textit{ Disambiguation; Distributed Training and Indexing}
    \end{itemize}
\item~\textbf{Yahoo Labs}: \href{https://research.yahoo.com/research-areas/advertising-science}{Ad-Predict Team}\hfill{\small\textit{(June - Dec'12)}}
\vspace{-1mm}
\begin{itemize}[leftmargin=*]\compresslist
        \item[]\small\textit{Themes: Display Ad-Platform; User-Response Prediction}
    \end{itemize}
\item~\textbf{Yahoo R\&D}: User Data \& Analytics Team \hfill{\small\textit{(Jan - June'12)}}
\vspace{-1mm}
\begin{itemize}[leftmargin=*]\compresslist
        \item[]\small\textit{Themes: Search Ad-Platform; User-Response Prediction; Automated Account Optim.}
    \end{itemize}
\end{itemize}

\vspace{-0.1cm}
\section{\mysidestyle Teaching Experience} 
\textsf{\textbf{Teaching Assistant}}:
\begin{itemize}[leftmargin = 0.7cm]\compresslist
\item~\textbf{UIUC}: Machine Learning, CS446 \hfill{\small\textit{(Aug - Dec'16)}}\vspace{-1mm}
\item~\textbf{IIT-Bombay}: Web Search and Mining, CS635 \hfill{\small\textit{(July - Nov'13)}}\vspace{-1mm}
\item~\textbf{BITS-Pilani}: Operating Systems, CS C372 \hfill{\small\textit{(Aug - Dec'11)}}
\end{itemize}

\vspace{-0.1cm}
\section{\mysidestyle Recent\\ Projects}
\textsf{\textbf{Unsupervised Text Classification}} \hfill\textit{\small(Aug'15 - Present)}
\\ {\textit{Guide: \href{http://www.cis.upenn.edu/~danroth/}{Prof. Dan Roth}, UIUC}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#dataless}{Web}}
\vspace{0.05cm}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=0.7cm]\compresslist
    \item[--] Key \href{https://cogcomp.org/page/project_view/6}{idea} is to embed documents \& topics using World Knowledge, and then compute similarity.
    \item[--] Developed new topic-sensitive \href{https://shatu.github.io/\#topic-emb}{word} and \href{https://shatu.github.io/\#entity-emb}{entity} embeddings by augmenting the Word2Vec loss, and used their composition to represent documents.
    \item[--] Upon identifying the need to learn the composition itself, modeled it as a One-shot Topic Classification problem using Distant Supervision from Wikipedia.
    \item[--] An empirical study of architectures revealed the importance of hierarchical modeling \& attention.
    \item[--] Currently using VGG-style networks with skip connections to learn topic-sensitive document embeddings from Wikipedia, where the Wikipedia categories are the labels.
\vspace{0.05cm}
    
\end{itemize}

\vspace{-0.1cm}    
\textsf{\textbf{Conditional Text Generation}} \hfill\textit{\small(Jan - May'17)}
\\ {\textit{Guide: \href{http://slazebni.cs.illinois.edu/}{Prof. Svetlana Lazebnik}, UIUC}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#textGen}{Web}}
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
\item[--]Experimented with Conditional GANs and VAEs for sentiment-conditioned review generation. \item[--]Experimented with both Policy-Gradient and Gumbel-Softmax, and used Curriculum Learning with a conditional language model to bootstrap the GANs.
\end{itemize}

\newpage
\vspace{-0.1cm}    
\textsf{\textbf{Joint NER, Relation Extraction and CoReference Resolution}} \hfill\textit{\small(Jan - May'16)}
\\ {\textit{Guide: \href{http://www.cis.upenn.edu/~danroth/}{Prof. Dan Roth}, UIUC}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#cs546}{Web} $|$ \myhref[darkblue]{https://github.com/shatu/Joint-NER-RelEx-Coref}{Github}}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
\item[--]Aim was to try out joint modeling of NER, Relation Extraction and CoRef with constraints.
\item[--]Simple coupling of classifiers without constraints showed poor performance.
\item[--]Developed a framework for joint training with \href{https://en.wikipedia.org/wiki/Constrained_conditional_model}{Constrained-Conditional Models}, using \href{https://github.com/CogComp/illinois-sl}{Illinois-SL} and \href{https://github.com/CogComp/cogcomp-nlp}{CogComp-NLP}. 
\end{itemize}


\section{\mysidestyle Past\\Projects}
\textsf{\textbf{Agile NERD for KB-Lifecycle}}\hfill\textit{\small(Aug'14 - April'15)}
\\ {\textit{Guide: \href{https://people.mpi-inf.mpg.de/~weikum/}{Prof. Gerhard Weikum}, \href{https://sites.ualberta.ca/~denilson/}{Prof. Denilson Barbosa}, MPI}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#mpi}{Web}}
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
\item[--]Identified the problem of separating mentions of emerging entities from mentions worthy of abstention as the key hurdle in achieving real-time KBs and iterative entity annotation on corpus. 
\item[--]Used the disagreement between an ensemble of annotators to signal abstention on a given mention.
\end{itemize}

\vspace{-0.2cm}    
\textsf{\textbf{Scalable Entity Disambiguation and Search}}\hfill\textit{\small(Jan'13 - June'14)}
\\ {\textit{Guide: \href{https://www.cse.iitb.ac.in/~soumen/}{Prof. Soumen Chakrabarti}, IIT-Bombay}}\hfill{\myhref[darkblue]{https://shatu.github.io/\#iitb}{Web} $|$ \myhref[darkblue]{https://shatu.github.io/papers/Web-scale_Entity_Annotation_Using_MapReduce.pdf}{Publication} $|$ \myhref[darkblue]{https://www.cse.iitb.ac.in/~soumen/doc/CSAW/}{CSAW}}
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
    \item[--]Designed a scalable entity annotation and indexing framework in Hadoop. Designed custom-key partitioning strategies to mitigate the load-skew problem of a simple MapReduce implementation.
    \item[--]Improved the accuracy of the entity disambiguation system by extracting more training data from Wikipedia and engineering features.
    \item[--]Developed hadoop-based solutions for distributed training of millions of models. 
\end{itemize}

\vspace{-0.2cm}
\textsf{\textbf{User Response Prediction for Non-Guaranteed Display Ad Delivery}}\hfill\textit{\small(June - Dec'12)}
\\ {\textit{Guide: \href{http://www.pmg.it.usyd.edu.au/}{Prof. Sanjay Chawla}, \href{https://www.cse.iitb.ac.in/~shivaram/}{Prof. Shivaram Kalyanakrishnan}, Yahoo Labs}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#labs}{Web}}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
    \item[--]Improved the accuracy of the user-click prediction model by mining new features. 
    \item[--]Analyzed Petabytes of data for feature signal \& coverage.
    \item[--]Used that analysis to find a training data partitioning strategy that showed promise when different models were trained on those different partitions.
\end{itemize}

\vspace{-0.2cm}    
\textsf{\textbf{Automated Campaign Optimization for Search Advertising}}\hfill\textit{\small(Jan - June'12)}
\\ {\textit{Guide: Ajay Sharma, Director, UDA, Yahoo R\&D}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#uda}{Web}}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
    \item[--]Protoyped a tool that automated the account optimization for advertisers. 
    \item[--]Developed models for predicting \#impressions, \#clicks, \#conversions, and handled sparsity issues by using community detection algorithms to cluster competitors together. 		\item[--]Ultimately, given a budget, the tool used resource allocation algorithms to select appropriate bid amounts for various targeting combinations.
\end{itemize}

\vspace{-0.2cm}    
\textsf{\textbf{Web Search Personalization on the Client-side}}\hfill\textit{\small(Aug'10 - Dec'11)}
\\ {\textit{Guide: Prof. Mangesh Bedekar, BITS-Pilani}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#bits}{Web}}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
    \item[--]Prototyped a browser extension that modeled the user intention and re-ranked search results on the client-side. 	\item[--]A neural model was learned to identify useful pages from user's browsing history using user's browsing patterns as features. 
    \item[--]Those pages were then used to build a user profile over time, which was ultimately used to personalize the search results on the client-side.
\end{itemize}


\vspace{-0.2cm}    
\textsf{\textbf{Online Comprehensive Examination Software}}\hfill\textit{\small(May - July'10)}
\\ {\textit{Guide: P.B. Kotur, Director, Talent Transformation, Wipro InfoTech}} \hfill{\myhref[darkblue]{https://shatu.github.io/\#wipro}{Web}}
\normalsize
\vspace{0.05cm}
\begin{itemize}[leftmargin=*]\compresslist
    \item[] Developed a Subjective Online Examination application using JSP and Servlets.
\end{itemize}

\section{\mysidestyle Relevant Coursework} 
Machine Learning, NLP, Structured Learning, Recent Trends in Deep Learning, Graphical Models, Web Search \& Mining, Organization of Web Information, Advanced Data Mining

% \vspace{-0.2cm}    
% \section{\mysidestyle Test Scores}
% \textbf{GRE:} 330/340  $|$  \textbf{TOEFL:} 111/120

\vspace{-0.1cm}
\section{\mysidestyle Talks}
\vspace{0mm}
%\begin{itemize}[leftmargin=*]\compresslist
%\item 
\textit{``Web-scale Entity Annotation Using MapReduce"}. \\
\textbf{\ Invited Talk}: Yahoo \href{https://www.eventbrite.com/e/yahoo-summer-school-2013-registration-6688943811#}{Summer School} on IR \& the Semantic Web, IISc, Bangalore\hfill{[\myhref[darkblue]{https://shatu.github.io/talks/HadoopAnnot.ppt}{Slides}]}
%\end{itemize}

\vspace{-0.2cm}    
\section{\mysidestyle References} 
\textbf{\textsf{\href{http://www.cis.upenn.edu/~danroth/}{Dan Roth}}}, \textit{Professor, UIUC} | \href{mailto:danr@illinois.edu}{danr@illinois.edu}\hfill{\textit{[Thesis adviser]}}
\vspace{0.8mm}
\\
\textbf{\textsf{\href{https://www.cse.iitb.ac.in/~soumen/}{Soumen Chakrabarti}}}, \textit{Associate Prof., IIT-Bombay} | \href{mailto:soumen@cse.iitb.ac.in}{soumen@cse.iitb.ac.in}\hfill{\textit{[R.A. adviser]}}
\vspace{0.8mm}
\\
\textbf{\textsf{\href{https://sites.ualberta.ca/~denilson/}{Denilson Barbosa}}}, \textit{Associate Prof., Univ. of Alberta} | \href{mailto:denilson@ualberta.ca}{denilson@ualberta.ca}\hfill{\textit{[R.A. adviser]}}
\vspace{0.8mm}
\\
\textbf{\textsf{\href{https://www.cse.iitb.ac.in/~shivaram/}{Shivaram Kalyanakrishnan}}}, \textit{Assistant Prof., IIT-Bombay} | \href{mailto:shivaram@cse.iitb.ac.in}{shivaram@cse.iitb.ac.in}\hfill{\textit{[R.A. adviser]}}


\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF
